\PassOptionsToPackage{table,dvipsnames}{xcolor}

\documentclass[sigconf,balance=false]{acmart}

\usepackage{popets}

\input{top-matter/header.tex}
\input{top-matter/macros.tex}

\newif\ifsubmission
\submissionfalse

% Copyright
\setcopyright{popets}
\copyrightyear{YYYY}

% Issue info
\acmYear{YYYY}
\acmVolume{YYYY}
\acmNumber{X}
\acmDOI{XXXXXXX.XXXXXXX}
\acmISBN{}
\acmConference{Proceedings on Privacy Enhancing Technologies}
\settopmatter{printacmref=false,printccs=false,printfolios=true}

\settopmatter{authorsperrow=4}

\begin{document}
\title{Beyond the Output: Inference Attacks on Private Set Union and Multi-Key Private Matching}

%%%%%%%%%%%%%%%% Authors' Info %%%%%%%%%%%%%%%%%
\author{Andrea Raguso}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{ETH Zurich}
  \city{Zurich}
  \state{}
  \country{Switzerland}}

\author{Francesca Falzon}
\affiliation{%
  \institution{ETH Zurich}
  \city{Zurich}
  \state{}
  \country{Switzerland}}

\author{Tianxin Tang}
\affiliation{%
  \institution{University of Glasgow}
  \city{Glasgow}
  \state{}
  \country{UK}}

\author{Kenneth G. Paterson}
\affiliation{%
  \institution{ETH Zurich}
  \city{Zurich}
  \state{}
  \country{Switzerland}}

\renewcommand{\shortauthors}{Raguso et al.}

\input{content/abstract}

\keywords{private set union, private set intersection, multi-key private
  matching, attacks, multi-party computation}

\maketitle

\input{content/introduction.tex}
\input{content/prelims.tex}
\input{content/recovery-goals.tex}
\input{content/psu-attacks.tex}
\input{content/MRR.tex}
\input{content/VIR.tex}
\input{content/MSR.tex}
\input{content/evaluation.tex}
\input{content/conclusion.tex}

\section*{Ethical Considerations}
This work assumes intended use of the PSU, PSU-CA, and Meta’s MKPM protocols. Our analysis leverages intrinsic vulnerabilities in the functionality outputs and does not break the protocols themselves or the underlying cryptographic primitives. 

\heading{Use of Synthetic Data.}
Our experiments use only synthetic data, generated either by (a) sampling numerical values from integer intervals or (b) using the Python Faker library~\cite{faker}. This ensures that no personally identifying or sensitive data is leaked and eliminates any risk of harm to individuals or groups.

\heading{Disclosure.}
We contacted the authors of the MKPM work~\cite{MKPMC} on 27.02.2026, 
to share our findings and a preprint of this work. We received an official response on 02.03.2026 from the developers acknowledging the leakage of the protocol. They further stated that MKPM is not currently being used in any production systems.

Our analysis was thus conducted on the functionality of a protocol that, at the time of writing, is not deployed and therefore does not pose any negative impacts on live systems or stakeholders.

\section*{Open Science}
In accordance with the open science policy, our code base has undergone artifact evaluation. Our artifact contains the code for our attacks and for generating the synthetic data, as well as instructions on how to run the code. The open source respository can be found here: \href{https://github.com/deRaguso/mkpid-attacks-artifact}{https://github.com/deRaguso/mkpid-attacks-artifact}.


\begin{acks}
Francesca Falzon was supported by the Zurich Information Security and Privacy Center (ZISC).
Tianxin Tang was partially supported by an NWO VIDI grant (Project No. VI.Vidi.193.066).
The authors would also like to thank the reviewers for their helpful feedback, including their suggestion for simplifying the PSU attack.
The authors acknowledge the use of generative AI tools solely for basic editing
of the text and grammar. 
\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{cryptobib/abbrev3,cryptobib/crypto,references}

\appendix
\input{content/ap-prelims.tex}
\input{content/ap-recovery.tex}
\input{content/ap-guos.tex}
\input{content/ap-psu.tex}
\input{content/ap-skpm.tex}
\input{content/ap-MRR.tex}
\input{content/ap-VIR.tex}
\input{content/ap-MSR.tex}
\input{content/ap-evaluation.tex}
\end{document}