\section{Additional Content for MRR Attack}\label{ap:MRR}

\subsection{Proof of Theorem~\ref{thm:psu-mkpm:correctness}}
\label{sec:psu-mkpm:correctness}

In order to prove correctness, we must first prove the following two lemmas.:

\begin{lemma}
	\label{lem:set_isolation_determinism}
	Let $X, Y \subseteq \Ispace{}^{\leq \lambda}$ be two sets of records. 
	If $X$ is $Y$-isolated, 
	the cardinality of $\UID$ output by $\calF_\MKPM(X; Y)$ (Figure~\ref{fig:MKPM}) 
  is consistent across multiple evaluations.
\end{lemma}

\begin{proof}
	For any $\bx \in X$, let $Y_\bx\subseteq Y$ denote the set of records in $Y$
  that share at least one identifier with $\bx$,
	i.e., 
  \[
    Y_\bx := \{\by \in Y \setdsc \exists i, j \in \NN \text{ s.t. } \bx[i] = \by[j]\}.
  \]
	If $X$ is $Y$-isolated, then by definition, we have that $Y_\bx \cap Y_{\bx'} = \emptyset$ 
  for any $\bx, \bx' \in X$ such that $\bx \neq \bx'$. 
	Therefore, there exist no two records in $X$ that could be 
  matched with the same record in $Y$.
	
	We first consider sets $Y_\bx$ that are not empty.
	Since $\bx$ can only be matched with some $y \in Y_\bx$ and all $y \in Y_\bx$ 
  can only be matched with $\bx$,
	$\match$ (Figure~\ref{fig:match_logic}) will match $\bx$ with exactly one 
  $\by_\bx \in Y_\bx$, which are assigned the same UID 
  (line~\ref{lin:match_common_uid}).
	All other $\by \in Y_\bx\setminus\{\by_\bx\}$ will remain unmatched 
  and are assigned a unique UID (line~\ref{lin:match_unmatched_P_uid}).
  Furthermore, all $\by \in Y$ which do not belong to any $Y_{\bx'}$ 
  for some $\bx' \in X$ will also remain unmatched and are 
  assigned a unique UID (also line~\ref{lin:match_unmatched_P_uid}).
	Lastly, all $\bx\in X$ for which $Y_\bx = \emptyset$ will remain 
  unmatched and receive a distinct UID (line~\ref{lin:match_unmatched_C_uid}). 
	
	Thus, $\UID$ contains one UID for each $\by\in Y$ and one UID for 
  each unmatched $\bx\in X$, i.e.,
	$|\UID| = |Y| + |\{\bx \in X \setdsc Y_\bx = \emptyset\}|$.
	This is independent of the order of the records in $X$ and $Y$ and
	also independent of the shuffling done before the matching step in $\MKPM$.
	Since $\MKPM$ only uses randomness to shuffle the inputs, the lemma follows.
\end{proof}

\begin{lemma}
  \label{lem:set_isolation_inference}
  Let $X$ and $V\subseteq \Ispace{}^{\leq \lambda}$ be two sets of records and
  let $X_1$ and $X_2$ be a partition of $X$.  Moreover, let
  $(\UID, \MX) \sample \calF_{\MKPM}(X; Y)$ and
  $(\UID_i, M_{X,i}) \sample \calF_{\MKPM}(X_i; Y)$ for $i \in \{1,2\}$.  If $X$
  is $V$-isolated, we have $|\UID| = |\UID_1| + |\UID_2| - |V|$.
\end{lemma}

\begin{proof}
We show this by induction on $|X_1|$.
If $|X_1| = 0$ all records of $Y$ are unmatched and, thus, $|\UID_1| = |Y|$.
Note that $X_2 = X$ and thus we have $|\UID| = |\UID_2| = |\UID_2| + |\UID_1| - |Y|$.
In the first equality, we use Lemma~\ref{lem:set_isolation_determinism}. 

Assume $|X_1| = n_1$ for some $n_1 > 0$ and $|\UID| = |\UID_1| + |\UID_2| - |Y|$.
Since $X_1$ and $X_2$ form a partition of $X$, we must move a record from $X_2$ to $X_1$ to achieve $|X_1| = n_1+1$. Note that $|\UID|$ remains unchanged due to Lemma~\ref{lem:set_isolation_determinism}.
Let $\bx \in X_2$ and let $X'_1 = X_1 \cup \{\bx\}$ and $X'_2 := X_2 \setminus \{\bx\}$.
Moreover, let $\UID'_1$ and $\UID'_2$ be the sets of UIDs resulting from evaluating $\calF_{\MKPM}(X'_1, Y)$ and $\calF_{\MKPM}(X'_2, Y)$. 

We distinguish two cases.

\textbf{Case 1:} If no identifier of $\bx$ occurs in $Y$, $\bx$ was assigned its own UID.
Therefore, $|\UID'_1| = |\UID_1| + 1$ and $|\UID'_2| = |\UID_2| - 1$, which implies the claim.
	
\textbf{Case 2:} For the second case, assume $\bx$ shares some identifiers with $n^*$ records of $Y$. Call this set $Y_\bx$.
Since $X$ is $Y$-isolated, all records $\by \in Y_\bx$ only share identifiers with $\bx$,	but no other $\bx'\in X_2$.
Thus, $\bx$ is matched with some $\by^* \in Y_\bx$,
i.e., $\bx$ and $\by^*$ are assigned the same $\uid \in \UID_2$. After removing $\bx$ from $X_2$, $\by^*$ will still be assigned some $\uid' \in \UID'_2$, which it does not share with any $\bx' \in X'_2$, again since $X$ is $Y$-isolated. 
Therefore, $|\UID_2| = |\UID'_2|$. 
Similarly, since $\bx\not\in X_1$, no $\by\in Y_\bx$ and $\bx' \in X_1$ are assigned the same $\uid \in \UID_1$.
By the definition of $Y_\bx$ and since $X$ is $Y$-isolated, $\bx$ will be assigned the same $\uid\in \UID'_1$
as some $\by\in Y_\bx$ after being added to $X_1$, implying $|\UID_1| = |\UID'_1|$.

The claim then follows.
\end{proof}


We can now use the above lemmas to finally prove Theorem~\ref{thm:psu-mkpm:correctness}.


\begin{proof}
Let the output from $\PSUCAattack^{\calF_{\MKPM}(\cdot, V)}(T)$ be the two sets \posSet{} and \negSet{}.
Note all records of $T$ are contained in some subset $T_c\subseteq T$ that will eventually reach line~\ref{lin:PSUCA_add_condition}, since the attack only terminates once the priority queue is empty. 
Therefore, every record of $T$ is added to either \posSet{} or \negSet{}. For any $T_c$ reaching line~\ref{lin:PSUCA_add_condition} we have that either (1) $k_c = |T_c|$ or (2) $k_c  = 0$ by the loop condition on line~\ref{lin:PSUCA_inner_while_condition}.
Let $\UID_c$ result from evaluating $\calF_{\MKPM}(T_c, V)$.

By Lemma~\ref{lem:set_isolation_inference} we have $k_c = |T_c| + |V| - |\UID_c|$.
\begin{description}
  \item[Case 1:] If $k_c = |T_c|$, then we have $|\UID_c| = |V|$, i.e., all records of $T_c$ are matched. Since records are only added to \posSet{} if this case applies, we have $\posSet \subseteq T \sqcap V$.
  %%
  \item[Case 2:] If $k_c = 0$, then $|\UID_c| = |T_c| + |V|$, i.e., no records of $T_c$ were matched. Therefore, no record in $T_c$ shares any identifiers with any record in $V$.
  Since records are only added to \negSet{} if this case applies, we have $\negSet \subseteq T \setminus (T \sqcap V)$. 
\end{description}

We have therefore shown that $\posSet$ only contains matchable records, $\negSet$ only contains non-matchable records and that every record in $T$ is contained in either $\posSet$ or $\negSet$.
\end{proof}