 
\section{Introduction}
\label{sec:introduction}
Functionality leakage is an inherent feature of systems, such as secure multi-party computation (MPC), that allow two or more parties to compute over private inputs. Until recently, MPC primitives were largely theoretical, and their security definitions reflected this focus: standard MPC security aims to ensure that the only information leaked is the functionality output.

Today, these primitives are increasingly deployed. For example, Google’s Private Join and Compute protocol uses MPC for ad-conversion measurement~\cite{googlePJC}, and Coinbase's MPC wallet employs MPC to split a client's private key into two shares---one held by the client and the other by Coinbase~\cite{Coinbase}. At the same time, it is well known that given a function and access to input-output pairs, an adversary can infer additional information about the inputs. This information leakage is intrinsic to the functionality and not a failure of the protocol to meet its defined security. The growing adoption of MPC protocols thus makes it critical to understand what information can be inferred by participants and under which threat models such leakage becomes practically significant. 

Among the most widely studied and deployed MPC protocols are set-operation functionalities, such as private set intersection (PSI), which allow parties to privately compute the intersection of their datasets. PSI-like functionalities have been extensively explored in both protocol design and attack analysis (see Section~\ref{sec:related-work}). However, prior cryptanalytic work that considers adversaries who honestly execute the protocol and seek to infer information from the output is narrow in scope, focusing almost exclusively on PSI-like protocols~\cite{USENIX:GHLWJL22, NDSS:JiaDuYan24, USENIX:FalTan25}. This leaves a broad range of other functionalities largely unstudied in this adversarial setting.

\heading{Analyzing New Functionalities.} 
In this work, we focus on private set operations and more complex join functionalities. Our analysis begins with \emph{private set union (PSU)}, where two or more parties, each holding a set, compute and output the union without revealing anything else~\cite{USENIX:DZBC25,USENIX:TBZCC25,USENIX:JSZG24,USENIX:ZCLZL23,USENIX:JSZDG22,CCS:GNBT25,CCS:ZCLPHW24,CCS:TCLZ23,ASIACCS:CSSW25,ASIACCS:BlaAgu12,AC:LiuGao23,AC:KRTW19,PoPETS:GaoNguTri24,ACNS:Frikken07,C:KisSon05,EC:PuJiaTri26,EC:PisTri26}. PSU aims to facilitate data sharing while preventing the disclosure of the records in the intersection. PSU has been proposed for various applications, including the private aggregation of IP block lists~\cite{USENIX:JSZDG22,AC:KRTW19}, hospital data~\cite{USENIX:JSZDG22}, and network traffic data~\cite{USENIX:BSMD10}. We also consider a PSU variant called \emph{PSU-Cardinality (PSU-CA)}, which computes and outputs the cardinality of the union, offering aggregate statistics without revealing the contents of the inputs~\cite{CCS:FMJS17, CANS:DeCGasTsu12}.

To enable richer private data analytics, database operations often go beyond basic set operations. For example, a company may wish to group information about the same individual across multiple databases, where each record contains a key (e.g., name) and associated attributes (e.g., email, credit score). If a key appears in the intersection, the corresponding attributes can be \emph{unioned} to complete the individual’s information. This functionality, known as a \emph{database join}, can be viewed as a rich generalization of PSI and PSU. 
%Private database joins have been studied in prior work (e.g., \cite{PoPETS:LehMouSid26, CCS:AHKNPT23, AC:KRTW19}).
In practice, more expressive operations such as multi-key joins are often required. Building on our analysis of PSU and PSU-CA, we further study the multi-key extension of Meta’s deployed Private-ID protocol, \emph{Multi-key Private Matching for Compute (MKPM)}~\cite{MKPMC}, to understand the security guarantees provided by such protocols.


\heading{Threat Model and Recovery.} 
In this work, we consider a realistic adversary who executes the protocol honestly but may craft its inputs to maximize the information it can infer about the other party’s data.
A simple illustration of this arises in PSU, which is designed to hide the intersection of the input sets. While the intended security goal is to disclose ``nothing beyond the output,'' even trivial queries can violate this guarantee. For example, an adversary could submit the empty set and immediately learn the other party’s entire input. Prior work, such as Frikken~\cite{ACNS:Frikken07}, addresses this problem by assuming thresholds or authorization mechanisms to prevent such pathological queries. In this work, we go further: we ask whether it is possible to circumvent these types of mitigation strategies.

Looking beyond simple, abstract functionalities to concrete protocol instantiations introduces additional subtleties. We explicitly separate the intended functionality (what is supposed to be computed) from additional protocol-specific leakage (e.g., set sizes and structural information). For example, many PSI/PSU schemes leak the parties’ input set sizes in addition to the intersection/union. In the case of Meta’s multi-key join protocol~\cite{MKPMC}, we also distinguish between the ideal multi-key matching functionality and the actual protocol leakage, which reveals extra information in exchange for efficiency.
This distinction motivates our two-part analysis of MKPM: one part considers the intended functionality, and the other considers all leakage available in a real protocol execution. Our analysis shows that attacks can become drastically more efficient when the adversary also learns this additional leakage. This highlights the importance of carefully characterizing protocol-specific leakages, which is often under-specified in the literature, as was the case for MKPM~\cite{MKPMC}.


% We identify several subtleties that are not fully addressed by their security proof sketch, including the treatment of repeated identifiers and certain syntactic inconsistencies. 
% is an important distinction between analyzing a generic PSU functionality and analyzing a concrete multi-key join protocol. We therefore divide our analysis into two parts: one that considers only the ideal functionality, and another that considers all information available in a real protocol execution.

% Moreover, the protocol reveals additional information beyond the intended output: the computing party learns a renamed and shuffled copy of both input sets, enabling it to infer the matching pattern between them. To reason about this, we explicitly separate the intended functionality (what is supposed to be computed) from additional leakage (e.g., set sizes and structural information), and then study what an adversary can recover from the latter.

% In the case of MKPM, because it is a concrete protocol rather than an abstract functionality, we also consider the leakage that arises from its specific design. This analysis clarifies what information can be learned beyond the intended output and highlights potential risks that should be carefully considered prior to deployment. 




\subsection{Contributions}

We present seven attacks that reveal the fundamental limitations in how existing PSU and multi-key join functionalities protect input privacy.
Our attacks are summarized in Table~\ref{tab:attack_comparison}.

We consider an adversary that participates in the two-party protocol, honestly executes it, and learns the output, but may maliciously craft its input to maximize information gained. As in prior work~\cite{USENIX:GHLWJL22, NDSS:JiaDuYan24,USENIX:FalTan25}, we assume that the adversarial party, $\tP_1$, holds a \textbf{target set} $T$ it seeks to learn about. The honest party, $P_2$, holds the \textbf{recovery set} $Y$.
The input structure depends on the functionality. For PSU and PSU-CA, $T=\{t_i\}_{i\in[n]}$ and $Y=\{y_k\}_{k\in[m]}$ are sets of values. For MKPMC, $T=\{\bt_i\}_{i\in[n]}$ and $Y=\{\by_i\}_{i\in[m]}$ are sets of records, where each record is a vector of values. As in prior work~\cite{USENIX:FalTan25}, we assume the recovery set is static. However, as we will see, many of our attacks do not rely on this assumption, as significant information can be recovered in one protocol invocation.


\heading{Attacks against PSU and PSU-CA.} 
Our first attack targets the PSU functionality. We show that when the protocol is invoked on two disjoint subsets forming a partition of $T$ (e.g., $T = X_1 \cup X_2$), the adversary can fully recover the intersection $T \cap Y$. \emph{This result significantly constrains how PSU can be safely used, both as a standalone protocol and as a component within more complex systems.}

Next, we consider PSU-CA. We demonstrate that although PSU-CA reveals only the cardinality of the set union, we can nevertheless recover the intersection $T \cap Y$ through a sequence of adaptively chosen queries. We establish a direct connection to PSI-CA, showing that any attack against PSI-CA (e.g.,~\cite{USENIX:GHLWJL22,NDSS:JiaDuYan24,USENIX:FalTan25}) can be transformed into an attack against PSU-CA using only three additional queries. \emph{This attack demonstrates how vulnerabilities in one functionality can be leveraged to attack a broader class of functionalities.}


\heading{Attacks against Meta's Multi-Key Private Match.} 
We next turn our attention to Meta’s multi-key join functionality~\cite{MKPMC} and present five concrete attacks. We begin by analyzing the intended functionality (without leakage) and show that, even under the most idealized output specification, an adversary can infer which records in $T$ share attribute values with records in $Y$.
We further establish a close relationship between PSU-CA and MKPM, demonstrating that our attack on PSU-CA can be directly leveraged to recover this information in the multi-key join setting.

The remaining attacks further exploit protocol-specific leakage. In particular, one attack recovers all values shared between $T$ and $Y$, while the final three attacks produce an exact reconstruction $R_Y$ of the records in $Y$, up to the shared values. These latter attacks are able to do so using a \emph{single} query.
\emph{Together, these results underscore the importance of explicitly modeling and cryptanalyzing seemingly benign, protocol-specific leakage that extends beyond the intended functionality.}

\heading{Experimental Evaluation.} 
To validate our findings, we implement all attacks and demonstrate their high practical efficiency. For example, our PSU attack scales to recovery sets of size $|Y| = 10^6$ elements, with runtimes ranging from \SI{0.74}{\second} to \SI{3.13}{\second}.
For adaptive attacks requiring multiple queries (e.g., PSU-CA and MKPM without leakage), the empirical query cost is significantly lower than the theoretical upper bound, demonstrating greater practical efficiency than theory alone suggests.

\heading{Broader Impact.} 
Finally, we discuss the broader implications of our attacks. We re-examine common mitigation strategies, such as rate limiting and input validation, and explain why these mechanisms may be insufficient against the adversaries considered in this work. 


\subsection{Related Work}\label{sec:related-work}

\input{tables/overview.tex}

The seminal works of Freedman, Nissim, and Pinkas~\cite{EC:FreNisPin04} and Agrawal, Evfimievski, and Srikant~\cite{SIGMOD:AgrEvfSri03} laid the foundations for modern private set intersection. Since then, a long line of work has proposed protocols for both PSI (e.g.,\cite{C:PRTY19,USENIX:PinSchZoh14, CCS:CheLaiRin17, CCS:DonCheWen13, FC:DeCTsu10, ASIACCS:Kerschbaum12, CCS:RosTri21, C:ChaMia20}) and PSU (e.g.,~\cite{USENIX:DZBC25,USENIX:TBZCC25,USENIX:JSZG24,USENIX:ZCLZL23,USENIX:JSZDG22,CCS:GNBT25,CCS:ZCLPHW24,CCS:TCLZ23}). More recent constructions extend PSI to support private computation over payloads on intersecting elements, such as sums~\cite{EUROSP:IKNPSSRSY20} and inner products~\cite{ASIACCS:CHIKT23,AC:LPRST21}.

The systematic study of attacks on set-operation functionalities was initiated by Guo et al.~\cite{USENIX:GHLWJL22}, who presented intersection-recovery attacks against PSI-CA, PSI-SUM, and Meta’s Private-ID~\cite{PMC}. Jiang et al.~\cite{NDSS:JiaDuYan24} strengthened these results by reducing the required number of queries. Falzon and Tang~\cite{USENIX:FalTan25} proposed attacks on Google’s Private Join and Compute (PJC)~\cite{AC:LPRST21} using combinatorial, statistical, and signal-processing techniques. In a complementary direction, Zinkus et al.~\cite{USENIX:ZinCaoGre23} described a generic approach to automatically quantify functionality leakage.

These attack works, however, largely focus on single-key or set-based operations and do not analyze more complex matching and join protocols on multi-key tables. For example, subsequent work extended Private-ID to support multi-key datasets~\cite{MKPMC}, which we study in this work. Other protocols consider different models, such as delegation of computation to an untrusted third party~\cite{PoPETS:MMTSBC24}, joins across multiple parties~\cite{PoPETS:LehMouSid26}, or secret-shared outputs to enable further downstream computation~\cite{CCS:MohRinRos20,IDCloak}. Asharov et al.~\cite{CCS:AHKNPT23} proposed the first maliciously secure protocols that support JOIN and GROUP-BY (aggregation). However, attacks involving adversarially chosen inputs and repeated executions often fall outside the explicit threat models of these works, leaving their resilience to the kinds of inference attacks we study as an open question.





% Recent focus of cryptographic research has shifted from conventional
% all-or-nothing security to allowing secure computation on private data. This
% change is reflected by a plethora of work on secure two-party computation (2PC)
% and multi-party computation (MPC). In particular, multiple functionalities have
% been introduced and deployed in the real world \cite{}. These include basic set
% operations, such as private set intersection (PSI) and private set union (PSU).

% At the functionality level, the security goals of PSI and PSU are subtly different. PSI aims to reveal which elements lie in the intersection, whereas PSU aims to hide this information and reveal only the union. In principle, both are intended to reveal ``nothing beyond the output.'' However, trivial queries already show that additional constraints are needed: in PSU, an adversary could input the empty set and learn the other party’s entire input. Frikken~\cite{ACNS:Frikken07}, The usual justification is that thresholds or authorization mechanisms restrict such pathological inputs. In this work, we ask whether it is still possible to circumvent these mitigation mechanisms and recover the underlying set.

%\subsubsection{Attacks.}  

% \subsubsection{Protocols.} 
% The seminal works of Freedman, Nissim, and Pinkas~\cite{EC:FreNisPin04} and Agrawal, Evfimievski, and Srikant~\cite{SIGMOD:AgrEvfSri03} laid the foundations for modern private set intersection and private database operations. Kissner and Song~\cite{C:KisSon05} introduced a framework for privacy-preserving set
% operations, including union, intersection, and element reduction. Since then, a long line of work has proposed protocols for both PSI
% (e.g.,\cite{C:PRTY19,USENIX:PinSchZoh14, CCS:CheLaiRin17, CCS:DonCheWen13, FC:DeCTsu10, ASIACCS:Kerschbaum12, CCS:RosTri21, C:ChaMia20}) and PSU (e.g.,~\cite{USENIX:DZBC25,USENIX:TBZCC25,USENIX:JSZG24,USENIX:ZCLZL23,USENIX:JSZDG22,CCS:GNBT25,CCS:ZCLPHW24,CCS:TCLZ23}). More recent constructions extend PSI to support private computation over payloads associated with intersecting values, such as the sum~\cite{EUROSP:IKNPSSRSY20} and inner product~\cite{ASIACCS:CHIKT23,AC:LPRST21}.

% Protocols supporting computations on tables as inputs have also been
% proposed. Buddhavarapu et al.~\cite{PMC} proposed two protocols: (i) Private-ID, which computes a set of pseudorandom universal identifiers corresponding to the records in the union of the parties’ inputs, and (ii) PS$^3$I, which outputs secret shares of the matched records. Subsequent work extends Private-ID to support multi-key datasets~\cite{MKPMC} and to enable delegation of the computation to an untrusted third party~\cite{PoPETS:MMTSBC24}.

% Mohassel et al.~\cite{CCS:MohRinRos20} proposed a protocol for SQL-like join and
% select queries and whose inputs and outputs can be secret shared between the
% parties. Similarly, IDCloak~\cite{IDCloak} privately computes an $n$-party join
% and outputs secret shares of the result. Asharov et al.~\cite{CCS:AHKNPT23}
% proposed the first protocols that support JOIN and GROUP-BY (i.e., aggregation)
% operations and are secure against malicious adversaries. Most recently, Lehmann
% et al.~\cite{PoPETS:LehMouSid26} described a protocol that enables multiple
% parties to provide a receiver with the inner joins over their respective
% datasets. \ff{include explanation of why these works are relevant; do they consider a different threat model? Leave open for investigation in future works?}

% \subsubsection{Attacks.}  The study of attacks against set-operation
% functionalities was initiated by Guo et al.~\cite{USENIX:GHLWJL22}, who
% presented two intersection-recovery attacks against the Private Set Intersection
% Cardinality (PSI-CA) and Private Set Intersection Sum (PSI-SUM)
% functionalities. This work was extended by Jiang et al.~\cite{NDSS:JiaDuYan24},
% who introduced new attacks on the same functionalities that required fewer
% queries. Most recently, Falzon and Tang \cite{USENIX:FalTan25} proposed a series
% of attacks on Google’s Private Join and Compute (PCJ)
% functionality~\cite{AC:LPRST21}, which takes as input two key-value stores and
% computes the inner product of the values associated with intersecting
% keys. In another line of work, Zinkus et al.~\cite{USENIX:ZinCaoGre23} described a generic approach for automatically quantifying the leakage of a given functionality.

