\section{Analysis of PSU and PSU-CA}
\label{sec:psu-psuca}
While PSU and PSU-CA have received increasing attention, the information leaked by their output remains largely unstudied. Frikken~\cite{ACNS:Frikken07} observed that submitting an empty set in PSU fully reveals the other party's input and proposed abort-based mitigations. Jia et al.~\cite{USENIX:JSZG24} further analyzed PSU leakage, showing that Guo et al.'s~\cite{USENIX:GHLWJL22} PSI-CA attack extends to certain PSU variants, even under early-abort conditions, and proposed an ``enhanced'' PSU functionality that delays protocol leakage to the end of protocol executions.

We show that such countermeasures are insufficient by introducing an intersection-recovery attack on PSU that uses only two queries and does not require the adversarial input to be empty or disjoint from the recovery set. We then prove that PSU-CA leaks at least as much information as PSI-CA by reducing any PSI-CA attack with $q$ queries to a PSU-CA attack with $q{+}3$ queries. %In the next section, we further show that our PSU-CA attack extends to Meta's $\calF_{\MKPM}$ functionality.

\subsection{Analysis of PSU}
\label{sec:psu-attack}
Recall that the corrupted party $\tP_1$ holds the target set $T$ and can invoke
$\calF_{\PSU}(X; Y)$ on arbitrary sets $X$ with a fixed $Y$. Its goal is to
recover $T \cap Y$. Our attack relies on the following observation:

\begin{proposition}\label{prop:PSU_recon_Y}
  Let $T$ and $Y$ be sets and $X_1 \cup X_2$ be a partition of $T$. It holds
  that $Y = (X_1 \cup Y) \cap (X_2 \cup Y)$.
\end{proposition}

Proposition~\ref{prop:PSU_recon_Y} follows directly from the fact that $X_1$ and $X_2$ are disjoint. 
The recovery set $Y$ can therefore be reconstructed with only two $\PSU$ queries.
Since the adversary knows $T$, the intersection $T \cap Y$, if needed, can then be computed easily.

We refer to this generic attack as $\PSUattack$. 
Note that it requires no special inputs such as the empty set, but works with any two inputs that are disjoint from each other. 
Specific mitigation strategies that focus on prohibiting such special inputs are therefore ineffective.
Allowing only one protocol execution per party is arguably not only unrealistic for many PSU deployment scenarios, but can also be easily circumvented via Sybil attacks.

% \begin{equation}
%   \label{eqn:PSU_basis}
%   X \cap Y = (X \cup Y) \setminus (Y \setminus X) \setminus (X \setminus Y).
% \end{equation} 

% From a $\PSU$ query, the adversary directly obtains $X \cup Y$ and can compute
% $Y \setminus X = (X \cup Y) \setminus X$. The remaining challenge is to
% determine $X \setminus Y$. To address this, we rely on two additional
% observations, with proofs deferred to
% Appendix~\ref{proof:PSU_difference_distributes}
% and~\ref{proof:PSU_comp_partial_difference}, respectively.

% \begin{proposition}\label{prop:PSU_difference_distributes}
%   Let $X$ and $Y$ be sets and $X_1 \cup X_2$ be a partition of $X$. It holds
%   that $X \setminus Y = (X_1 \setminus Y) \cup (X_2 \setminus Y).$
% \end{proposition}

% \begin{proposition}
%   \label{prop:PSU_comp_partial_difference}
%   Let $X$ and $Y$ be sets and let $X_1\cup X_2$ be a partition of $X$.
%   Furthermore, let $Z_1 := X_1 \cup Y$ and $Z_2 := X_2 \cup Y$. Then,
%   $X_1 \setminus Y = X_1 \setminus Z_2$ and
%   $X_2 \setminus Y = X_2 \setminus Z_1$.
% \end{proposition}

% We combine Propositions~\ref{prop:PSU_difference_distributes} and
% \ref{prop:PSU_comp_partial_difference} with the identity in
% Eq.~\ref{eqn:PSU_basis} to compute $X \cap Y$ using three evaluations of
% $\PSU$. Moreover, one evaluation can be saved: the full union can be derived
% from two partial unions, since $X \cup Y = (X_1 \cup Y) \cup (X_2 \cup Y)$.

% We refer to this generic attack as $\PSUattack$. Let $X_1$ and $X_2$ be disjoint
% sets forming a partition of the target set $T$, i.e., $X_1 \cap X_2 = \emptyset$
% and $X_1 \cup X_2 = T$. Then the adversarial party $\tP_1$ can recover the
% intersection by querying $\calF_{\PSU}(X_1;Y)$ and $\calF_{\PSU}(X_2;Y)$. We
% provide the pseudocode in Figure~\ref{fig:PSU_attack} in
% Appendix~\ref{ap:psu-attack-pseudocode}.

% \begin{theorem}
%   Let $T$ be the target set and $Y$ be the recovery set. The attack
%   $\PSUattack^{\calF_{PSU}(\cdot; Y)}(T)$ (Figure~\ref{fig:PSU_attack}) achieves
%   intersection recovery (Def.~\ref{def:intersection-recovery}).
% \end{theorem}
% \begin{proof}
%   The theorem follows from Propositions~\ref{prop:PSU_difference_distributes}
%   and \ref{prop:PSU_comp_partial_difference}.
% \end{proof}

\subsection{PSU-CA Attack}\label{sec:PSUCA_attack}
The cardinalities of the union and intersection of two sets are closely
related. We present a generic transformation that converts any intersection
recovery attack against PSI-CA (e.g.,~\cite{USENIX:GHLWJL22}) into one against
PSU-CA to recover the intersection.

Let $X$ and $Y$ be sets. Our attack relies on the following relation,
\begin{equation}\label{eqn:union_intersect_cardinalities}
  |X \cap Y| = |X| + |Y| - |X \cup Y|
\end{equation}

This enables a translation from PSU-CA to PSI-CA, and thus allows lifting any
PSI-CA intersection recovery attack to the PSU-CA setting.
A remaining challenge is that $|Y|$ is generally unknown. We therefore present
the following method to determine $|Y|$ with three $\PSUCA$ evaluations that
avoids the trivial solution of querying the empty set, i.e.,
$\calF_{\PSUCA}(\emptyset; Y)$.

\begin{proposition}\label{prop:PSUCA_comp_m}
  Let $X$ and $Y$ be two sets and let $X_1\cup X_2$ be a partition of
  $X$. Moreover, let $z:= |X \cup Y|$, $z_1 := |X_1 \cup Y|$ and
  $z_2 := |X_2 \cup Y|$. Then, we have $|Y| = z_2 - (z - z_1)$.
\end{proposition}
 
The proof is provided in Appendix~\ref{proof:PSUCA_comp_m}. Thus, with three
additional $\calF_{\PSUCA}$ evaluations at the start of the attack, the
adversary can simulate the $\calF_{\PSICA}$ functionality. In particular, for
any PSI-CA attack, the adversary can replace each query
$z\gets \calF_{\PSICA}(X;Y)$ with $z'\gets \calF_{\PSUCA}(X;Y)$ and then compute
$z$ as $|X|+|Y|-z'$.

We state our result in the following theorem:
\begin{theorem}\label{thm:PSICA-to-PSUCA}
  For every adversary $\adv$ such that
  $\adv^{\calF_{\PSICA}(\cdot; Y)}(T) = T \cap Y$ which makes $q$ $\PSICA$
  queries, there is an efficient adversary $\bdv$ with access to
  $\calF_{\PSUCA}(\cdot; Y)$ which recovers $T \cap Y$ and makes $q + 3$
  $\PSUCA$ queries.
\end{theorem}

The proof is given in Appendix~\ref{proof:PSICA-to-PSUCA}. In
Appendix~\ref{attack:PSUCA}, we describe and analyze
$\PSUCAattack$---an attack that uses the transformation described above to turn
the PSI-CA attack from Guo et al.\cite{USENIX:GHLWJL22} (See
Appendix~\ref{ap:guo_attack} for an overview) to one against PSU-CA.